---
title: "Homework 9"
author: "Jae Hoon Cho"
date: "November 13, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Submit your solution for the Problem 1 from Activity 9.

```{r}
library(microbenchmark)
x <- c(1:10000)

odd_count = function(x) {
  odd_num = 0
  for (i in 1:length(x)) {
    if (x[i] %% 2 == 1) odd_num = odd_num + 1
}
  return(odd_num)
}

odd_count2 <- function(x) {
  return(length(x[x %% 2 == 1]))
}

microbenchmark(odd_count(x), odd_count2(x))
```

2. Modify the sorting function (sort_vec) from “Assignment 8” (problem 3) so that it should take an additional argument ascending which causes sorting in increasing order when ‘ascending = TRUE’. In other words,

• sort_vect(c(3, 1, 2), ascending = TRUE) = (1, 2, 3)
• sort_vect(c(3, 1, 2), ascending = FALSE) = (3, 2, 1)

```{r}
SortVec <- function(x, ascending = T) {
# return a sorted vector in ascending order
  if (length(x) == 1) {
    return(x) 
  } else if (ascending == T) {
    for(last in length(x):2) {
      for(first in 1:(last - 1)) {
        if(x[first] > x[first + 1]) {
          temp <- x[first]
          x[first] <- x[first + 1]
          x[first + 1] <- temp
}}}
    return(x)
  } else {
    for(last in length(x):2) {
      for(first in 1:(last - 1)) {
        if(x[first] < x[first + 1]) {
          temp <- x[first]
          x[first] <- x[first + 1]
          x[first + 1] <- temp
}}}
    return(x)
  
    }}

test <- c(5,3,7,0,2,9,11,4,6)
SortVec(test, ascending = T)
SortVec(test, ascending = F)

```

3. Consider a simple random walk with starting point 0 and a step -1 or 1. Below is the code with dynamically allocated memory. Write your code with preallocated memory and compare time for both versions using system.time() function (use N = 1000, 10000 and 1000000).

```{r}
N = c(1000,10000, 10000000)
remove (data_series)
data_series = 0
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1)
}
})
```

```{r}
remove (data_series2)
data_series2 <- c(NA) 
length (data_series2) <- 10000000
system.time({for (i in 2:N){
data_series2[i] = data_series2[i-1] + sample(c(-1, 1), 1)
}
})
```

# It is odd. Preallocation did not work.



